FTLR proof cases

### 2018-06-25 fully-abstract-comp/ftlr-proof-cases.tex
Do a check of a first part of the FTLR call case.
Particularly, highlight the place where I think we need to use the reasonability of the ec.
Fix some minor things, point out some minor problems.

  In order to prove this, we first, we prove that one of the following holds:
  \lau{TODO: add $\neq$ failed to the cases that are not failed.}
  \begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
      % domi: this condition doesn't make syntactic sense and is also not used.
    % \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{[\aaddr_\stk,\eaddr_\stk]}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

  In case \ref{case:ftlr:failed}, both executions go to failed. In this case, we
  either assume that the target configuration terminates or that the source
  configuration terminates, but in either case it leads to a contradiction with
  the failing configuration.
  \\\\
  In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
  steps, so both directions of $\lro$ are trivially satisfied.
  \\\\
  In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to conclude
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]
  from the following facts:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}: Follows from the corresponding assumption of this lemma and
    the fact that $\Phi_S \nstep[1]{\ta,\stkb} \Phi_S'$ and
    Lemma~\ref{lem:ec-reasonable-antired},
    \ref{lem:ec-reasonable-downwards-closed}, and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$:
    Follows from the definition of $\updPcAddr{}$ and the assumptions of this case.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed} and the fact that integers are always in $\lrvg{\trust}$ by definition.
  \item $\memSat[n-1]{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item Theorem~\ref{thm:ftlr} holds for all $n'' < n-1$:
    follows from the corresponding assumption of this lemma, since $n - 1 < n$.
  \end{itemize}

  \lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.
    (I have done this, and it does not seem necessary (?))}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump.
    If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.}
  and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.}.
  as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n]{(\reg_S(r_i),\reg_T(r_i))} \in \lrrg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

  \begin{equation}
    \forall W' \future W_{R,1}, W_o, n' < n, \npair[n']{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \npair[n']{c_1,c_2,c_1',c_2'} \in \lrexj(W'\oplus W_o)\label{eq:ftlr:call:sealed-code-assump}
  \end{equation}
  Now construct $W_{R,1}'$ as follows:

  By Lemma~\ref{lem:nsub-and-nsup-std} and the safety assumption on the register-file, there exists $S \supseteq [\baddr_\stk, \eaddr_\stk]$ such that for some $R : S \fun \powerset{\nats}$ we have $\biguplus_{r \in S} R(r) \supseteq [\baddr_\stk,\eaddr_\stk]$ and for all $r$ in $S$ $\pwfree[W_{R,1}](r).H \nequal \stdreg{R(r),\gc}{\pur}.H$ and $|R(r)| = 1$ and $\pwfree[W_{R,1}](r) \text{ is address-stratified}$.
  Now define
  \[
    W_{R,1}' = W_{R,1}[\free.R^{-1}([\aaddr_\stk,\eaddr_\stk]) \mapsto \revoked][\priv.r_\var{priv\_stk} \mapsto (\stareg[(\ms_{\stk\_\priv,S},\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}),\gc]{\spa,\square},\aaddr+\calllen)]
  \]
  For a fresh $r_\var{priv\_stk}$.
  We know $W_{R,1}' \future W_{R,1}$ as the revoked regions must have been $\spatial$ in $W_{R,q}$ (as they are owned by the part of the world assigned to the stack-register in the register-file relation).
  The static region for the private stack is an extension of the old world.

  Pick this world as $W'$ in Eq~\ref{eq:ftlr:call:sealed-code-assump}
  . Let $W_{R,2}'$ be the same world but
  with the ownership of $W_{R,2}$ and pick it for $W_o$.
  Now use monotonicity of $H_\sigma$ with the above facts to get
  \[
    \npair[n-1]{c_1,c_2,c_1',c_2'} \in \lrexj(W_{R,1}'\oplus W_{R,2}')
  \]
  Now pick register files and memories such that they form $\Phi_S''$ (defined in
  the assumptions) and $\Phi_T''$ and for $W_R'$ and $W_M'$ (we define them below) show
  \begin{enumerate}[label=\roman*.]
  \item \label{case:ftlr:scall:world} $W_{R,1}'\oplus W_{R,2}' \oplus W_R' \oplus W_M'$
  \item \label{case:ftlr:scall:reg} $\npair[n-1]{(\Phi_S''.\reg,\Phi_T''.\reg)} \in \lrr(\{\rdata\})(W_R')$
  \item \label{case:ftlr:scall:mem} $\memSat[n-1]{\Phi_S''.\mem,\Phi_S''.\stk,\Phi_S''.\ms_\stk,\Phi_T''.\mem}{W_M'}$
  \end{enumerate}
  to get
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  as desired.
  It remains to show \ref{case:ftlr:scall:world}-\ref{case:ftlr:scall:mem}, but first we note that we can deduce the following: From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\sigrets',\_,M(r),\gc}$.
  Further by $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one $r \in S$ there is a $\mscode' \subseteq \mscode$, call this $r$ for $r_{\mscode'}$,\footnote{Follows from $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) = \ta$ and finally that $\mscode$ is part of $\ms_S$.}
  such that
  \begin{equation}
    \npair{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_,\gsigrets,\gsigcloss)\label{eq:ftlr:rretd:Hcode}
  \end{equation}
  where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  That is $\mscode'$ contains the call we are considering.
  This also entails
  \begin{equation}
    \label{eq:ftlr:code-comp-jud}
    \sigrets',\sigcloss' \vdash_\var{code\_comp} \mscode'
  \end{equation}
from \ref{eq:ftlr:rretd:Hcode} we also get
\begin{itemize}
\item $\dom(\mscode') \subseteq \ta$

@@

  Case \ref{case:ftlr:scall:reg}: We need to split the ownership of $W_R'$.
  From assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrr(W_R)$, we get a way to split the ownership of $W_R$.
  We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
  region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
  Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
  Finally, $\rretc$ maps to a world with the ownership of $W$.

  we split the world in the same way for the registers that remain unchanged, the
  result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
  This leaves the following cases:
  \begin{description}
  \item[Case $\rstk$:] Show:
    \[
      \npair[n-1]{(\stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1},((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1))} \in \lrv(W_{R,\rstk}')
    \]
    We know by Assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we know
    \[
      \npair[n]{(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk},((\rw, \linear), \baddr_\stk ,\eaddr_\stk, \aaddr_\stk)} \in \lrvg{\trust}(W_{R,\stk})
    \]
    which by the $\mathit{stackReadCondition}$ gives $S \subseteq \addressable{\linear,\pwfree}$ and $R : S \fun \powerset{\nats}$.
    We need to pick an $S'$ to argue
    \[
      \npair[n-1]{[\baddr_\stk,\aaddr_\stk-1]} \in \stackReadCond{W_{R,\rstk}'}
    \]
    To this end pick $S' = R^{-1}(\left(\bigcup_{r\in S} R(r) \right) \setminus [\aaddr_\stk,\eaddr_\stk])$ and $R'$ to be $R$ limited to $S'$.
    As we exclude all the revoked regions and the ownership otherwise remains the
    same in $W_{R,\rstk}'$ as in $W_{R,\rstk}$, the regions in $S'$ are exactly the same in the new world as they were in $W_{R,\rstk}$.
    So what we need to show follows immediately from
    \[
      \npair[n]{[\baddr_\stk,\eaddr_\stk]} \in \stackReadCond{W_{R,\rstk}}
    \]
    and by Lemma~\ref{lem:downwards-closed}.

@@

    Based on $H_\sigma^\var{code}$, there are three possible values for $\vsc_S'$ and $\vsc_T'$.
    In the first case, $\vsc_S'$ is a $\retptrc$ and $\vsc_T'$ is a capability with permission $\rx$.
    In this case, $\var{xjumpResult}$ will produce failed configurations which are trivially in the observation relation.
    In the next case, it is required that $\sigma' \in \sigcloss'$, but this
    cannot be the case as $\sigma' \in \sigrets'$ and we have $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$.
\lau{TODO I think this case should follow from $H^\var{code}$ and the comp-code judgement, but it does not.
      Specifically, the comp-code judgement (for now) does not require $\sigrets'$ and $\sigcloss'$ to be disjoint.}

>>>>

  In order to prove this, we first, we prove that one of the following holds:
  \begin{enumproof}
  \item \label{case:ftlr:failed} $\Phi_S \step[\gc] \failed$ and $\Phi_T
    \step[i] \failed$ for some $i$.
  \item \label{case:ftlr:halted} $\Phi_S \step[\gc] \halted$ and $\Phi_T \step\halted$
  \item \label{case:ftlr:get-and-arith-op} All of the following hold: (includes simple cases: gettype, geta, getb,
    gete, getp, getl, lt, plus, minus, one case of move that can be handled
    uniformly)
    \begin{itemize}
    \item $\Phi_S \step[\gc] \Phi_S'$
    \item $\Phi_T \step \Phi_T'$
    \item $\Phi_S' = \updPcAddr{\Phi_S\updReg{r}{z}} \neq \failed$
    \item $\Phi_T' = \updPcAddr{\Phi_T\updReg{r}{z}} \neq \failed$
    \item $z \in \ints$
    \end{itemize}
  \item \label{case:ftlr:call} All of the following hold:
    \begin{itemize}
    \item $\callCond{\Phi_S,r_1,r_2,\offpc,\offsigma,\aaddr}$
    \item $r_1 \neq \rtmp{1}$ and $r_2 \neq \rtmp{1}$
    \item $\baddr \leq \aaddr \tand \aaddr + \calllen-1 \leq \eaddr$
    \item $\exec{\Phi_S(\pcreg)}$
    \item for all $i = 0..\calllen-1$, $\ms_T(\aaddr+i) = \ms_S(\aaddr+i) \in \ints$.
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\Phi_S \step[\gc] \Phi_S' \neq \failed$
    \item $\Phi_T \step \Phi_T' \neq \failed$
      % domi: this condition doesn't make syntactic sense and is also not used.
    % \item $\Phi_T' = \updPc{\Phi_T\updReg{\rtmp{1}}{z}}$
    \item $z \in \ints$
    \item $\Phi_S(r_1) = \sealed{\sigma,c_1}$
    \item $\Phi_S(r_2) = \sealed{\sigma,c_2}$
    \item $\nonExec{c_2}$
    \item $\Phi_S(\rstk) = \stkptr{\rw, \baddr_\stk, \eaddr_\stk, \aaddr_\stk}$
    \item $\baddr_\stk < \aaddr_\stk \leq \eaddr_\stk$
    \item $\Phi_S(\pcreg) = ((\perm,\lin),\baddr,\eaddr,\aaddr)$
    \item $w_1 = \linCons{c_1}$ and $w_2 = \linCons{c_2}$
    \item \[
        \begin{split}
          \Phi_S''.\reg = \Phi_S.reg      &[\rstk \mapsto \stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1}] \\
          &[\rretc \mapsto \sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr+\calllen)}]\\
          &[\rretd \mapsto \sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}] \\
          &[r_1,r_2 \mapsto w_1,w_2] \\
          &[\rtmp{1} \mapsto 0]
        \end{split}
      \]
    \item $\Phi_S''.\mem = \Phi_S.\mem$
    \item $\ms_{\stk\_\priv,S} = \Phi_S.\ms_\stk |_{[\aaddr_\stk,\eaddr_\stk]}\update{\aaddr_\stk}{42}$
    \item $\Phi_S''.\stk = ((\aaddr+\calllen),\ms_{\stk\_\priv,S}) :: \Phi_S.\stk$
    \item $\Phi_S''.\ms_\stk = \Phi_S.\ms_\stk -
      \Phi_S.\ms_\stk|_{[\aaddr_\stk,\eaddr_\stk]}$
    \item $\baddr \leq \aaddr+\offpc \leq \eaddr$
    \item $\mem(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr}$
    \item $\sigma' = \sigma_\aaddr + \offsigma$
    \item $\sigma_\aaddr \leq \sigma' \leq \sigma_\eaddr$

@@

  In case \ref{case:ftlr:failed}, both executions go to $\failed$.
  In this case, the result follows vacuously by definition of $\lrol$ and $\lror$.
  \\\\
  In case \ref{case:ftlr:halted}, both source and target configuration halts in 0
  steps, so both directions of $\lro$ are trivially satisfied.
  \\\\
  In case \ref{case:ftlr:get-and-arith-op}, we use the induction hypothesis to conclude
  \[
    \npair[n-1]{(\Phi_S',\Phi_T')} \in \lro
  \]
  from the following facts:
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n-1$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair[n-1]{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
    This follows from the corresponding assumption of this lemma and the fact that $\Phi_S \nstep[1]{\gc} \Phi_S'$ and Lemma~\ref{lem:ec-reasonable-antired}, \ref{lem:ec-reasonable-downwards-closed}, and \ref{lem:downwards-closed}.
  \item $\Phi_S'(\pcreg) = \Phi_T'(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$:
    Follows from the definition of $\updPcAddr{}$ and the assumptions of this case.
  \item $\npair[n-1]{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item $\npair[n-1]{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}, the definition of $\lrr$ and the fact that integers are always in $\lrvg{\trust}$ by definition.
  \item $\memSat[n-1]{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$:
    Follows from the corresponding assumption of this lemma using Lemma~\ref{lem:downwards-closed}.
  \item Theorem~\ref{thm:ftlr} holds for all $n'' < n-1$:
    follows from the corresponding assumption of this lemma, since $n - 1 < n$.
  \end{itemize}

  \lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.
    (I have done this, and it does not seem necessary (?))}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump. If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.} and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.} as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n]{(\reg_S(r_i),\reg_T(r_i))} \in \lrvg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

  \begin{equation}
    \forall W' \future W_{R,1}, W_o, n' < n, \npair[n']{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_o) \ldotp \npair[n']{c_1,c_2,c_1',c_2'} \in \lrexj(W'\oplus W_o)\label{eq:ftlr:call:sealed-code-assump}
  \end{equation}
  Now take $W_o = W_{R,2}$, take $n' = n-1$ and construct $W_{R,1}'$ as follows:

  By Lemma~\ref{lem:nsub-and-nsup-std} and the safety assumption on the register-file, there exists $S \supseteq [\baddr_\stk, \eaddr_\stk]$ such that for some $R : S \fun \powerset{\nats}$ we have $\biguplus_{r \in S} R(r) \supseteq [\baddr_\stk,\eaddr_\stk]$ and for all $r \in S$, $\pwfree[W_{R,1}](r).H \nequal \stdreg{R(r),\gc}{\pur}.H$ and $|R(r)| = 1$ and $\pwfree[W_{R,1}](r) \text{ is address-stratified}$.
  Now take $r_\var{priv\_stk}$ fresh and define
  \[
    W_{R,1}' = W_{R,1}[\free.R^{-1}([\aaddr_\stk,\eaddr_\stk]) \mapsto \revoked][\priv.r_\var{priv\_stk} \mapsto (\stareg[(\ms_{\stk\_\priv,S},\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}),\gc]{\spa,\square},\aaddr+\calllen)]
  \]
  We know $W_{R,1}' \future W_{R,1}$ as the revoked regions must have been $\spatial$ in $W_{R,q}$ (as they are owned by the part of the world assigned to the stack-register in the register-file relation).
  The static region for the private stack is an extension of the old world.

  Pick this world as $W'$ in Eq~\ref{eq:ftlr:call:sealed-code-assump}.
  Let $W_{R,2}'$ be the same world but with the ownership of $W_{R,2}$ and pick it for $W_o$.
  Now observe that also $W_{R,2}' \future W_{R,2}$ and use monotonicity of $H_\sigma$ with the above facts to get
  \[
    \npair[n-1]{c_1,c_2,c_1',c_2'} \in \lrexj(W_{R,1}'\oplus W_{R,2}')
  \]

  Now pick register files and memories such that they form $\Phi_S''$ (defined in
  the assumptions) and $\Phi_T''$ and for $W_R'$ and $W_M'$ (we define them below) show
  \begin{enumerate}[label=\roman*.]
  \item \label{case:ftlr:scall:world} $W_{R,1}'\oplus W_{R,2}' \oplus W_R' \oplus W_M'$ is defined.
  \item \label{case:ftlr:scall:reg} $\npair[n-1]{(\Phi_S''.\reg,\Phi_T''.\reg)} \in \lrr(\{\rdata\})(W_R')$
  \item \label{case:ftlr:scall:mem} $\memSat[n-1]{\Phi_S''.\mem,\Phi_S''.\stk,\Phi_S''.\ms_\stk,\Phi_T''.\mem}{W_M'}$
  \end{enumerate}
  to get
  \[
    \npair[n-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  as desired.

  It remains to show \ref{case:ftlr:scall:world}-\ref{case:ftlr:scall:mem}, but first we note that we can deduce the following: From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\sigrets',\_,M(r),\gc}$.
  Further by $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one $r \in S$ there is a $\mscode' \subseteq \mscode$, call this $r$ for $r_{\mscode'}$,\footnote{Follows from $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) = \ta$ and finally that $\mscode$ is part of $\ms_S$.}
  such that
  \begin{equation}
    \npair{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_,\gsigrets,\gsigcloss)\label{eq:ftlr:rretd:Hcode}
  \end{equation}
  where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  \dominique{How do we know $\ms_\code'$ contains [b,e] entirely?
    It does seem plausible that it contains the call entirely as well as $a + \offpc$ thanks to the code region's well-formedness.
  }
  That is: $\mscode'$ contains the call we are considering.
  This also entails
  \begin{equation}
    \label{eq:ftlr:code-comp-jud}
    \sigrets',\sigcloss' \vdash_\var{code\_comp} \mscode'
  \end{equation}
  from \ref{eq:ftlr:rretd:Hcode} we also get
\begin{itemize}
\item $\dom(\mscode') \subseteq \ta$

@@

  Case \ref{case:ftlr:scall:reg}: We need to split the ownership of $W_R'$.
  From assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we get a way to split the ownership of $W_R$.
  We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
  region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
  Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
  Finally, $\rretc$ maps to a world with the ownership of $W$.

  we split the world in the same way for the registers that remain unchanged, the
  result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
  \dominique{No: we need to use Lemma~\ref{lem:trusted-and-reasonable-is-untrusted} together with the reasonability of registers at a boundary crossing (if there is one).}

  This leaves the following cases:
  \begin{description}
  \item[Case $\rstk$:] Show:
    \[
      \npair[n-1]{(\stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1},((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1))} \in \lrv(W_{R,\rstk}')
    \]
    We know by Assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we know
    \[
      \npair[n]{(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk},((\rw, \linear), \baddr_\stk ,\eaddr_\stk, \aaddr_\stk)} \in \lrvg{\trust}(W_{R,\stk})
    \]
    which by the $\mathit{stackReadCondition}$ gives $S \subseteq \addressable{\linear,\pwfree}$ and $R : S \fun \powerset{\nats}$.
    We need to pick an $S'$ to argue
    \[
      \npair[n-1]{[\baddr_\stk,\aaddr_\stk-1]} \in \stackReadCond{W_{R,\rstk}'}
    \]
    To this end pick $S' = R^{-1}(\left(\bigcup_{r\in S} R(r) \right) \setminus [\aaddr_\stk,\eaddr_\stk])$ and $R'$ to be $R$ limited to $S'$.
    As we exclude all the revoked regions and the ownership otherwise remains the
    same in $W_{R,\rstk}'$ as in $W_{R,\rstk}$, the regions in $S'$ are exactly the same in the new world as they were in $W_{R,\rstk}$.
    So what we need to show follows immediately from
    \[
      \npair[n]{[\baddr_\stk,\eaddr_\stk]} \in \stackReadCond{W_{R,\rstk}}
    \]
    and by Lemma~\ref{lem:downwards-closed}.

@@

    Based on $H_\sigma^\var{code}$, there are three possible values for $\vsc_S'$ and $\vsc_T'$.
    In the first case, $\vsc_S'$ is a $\retptrc$ and $\vsc_T'$ is a capability with permission $\rx$.
    In this case, $\var{xjumpResult}$ will produce failed configurations which are trivially in the observation relation.
    In the next case, it is required that $\sigma' \in \sigcloss'$, but this
    cannot be the case as $\sigma' \in \sigrets'$ and we have $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$, which implies that $\sigcloss' \mathrel{\#} \sigrets'$.
